### 2018-03-11 paper/2-background.tex
Add an intuitive definition of a build system

@@

If the user modifies the sources of the utility library and runs \Make, it will
perform a \emph{full rebuild}, because all three tasks transitively depend on
the library, as illustrated in Fig.~\ref{fig-make}(b). On the other hand, if the
user modifies \cmd{main.c} then a \emph{partial rebuild} is sufficient: indeed,
the file \cmd{util.o} does not need to be rebuilt, since its inputs have not
changed, see Fig.~\ref{fig-make}(c). Note that if the dependency graph is
\emph{acyclic} then each task needs to be executed at most once. Cyclic task
dependencies are typically not allowed in build systems although there are rare
exceptions, see~\S\ref{sec-iterative-compute}.

@@

\begin{figure}[h]
\vspace{1mm}
\begin{subfigure}[b]{0.90\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/shake-example.pdf}}
\vspace{-1mm}
\caption{Dependency graph produced after the previous build.}
\vspace{1mm}
\end{subfigure}
\vspace{1mm}
\begin{subfigure}[b]{0.90\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/shake-example-rebuild.pdf}}
\vspace{-1mm}
\caption{Since \cmd{docs.txt} has changed, we rebuild \cmd{release.txt} and
\cmd{release.tar}, discovering a new dependency.}
\end{subfigure}
\vspace{-2mm}
\caption{Dynamic dependencies example: create \cmd{README} and add it to the
list of release documents \cmd{docs.txt}.\label{fig-shake}}
\vspace{-2mm}
\end{figure}

@@

\begin{minted}[xleftmargin=10pt]{haskell}
"release.tar" %> \_ -> do
    need ["release.txt"]
    files <- lines <$> readFile "release.txt"
    need files
    system "tar" $ ["-cf", "result.tar"] ++ files
\end{minted}

>>>>

We start by giving an intuitive definition of a build system. After providing
more context and examples in the rest of this section, we will be able to
develop a formal definition in~\S\ref{sec-general-build}.

\definition[Build system]{Given a description of tasks, a \emph{build system}
executes some of them in an order that respects their dependencies to produce a
specified output from supplied inputs.}
\label{def-build}

@@

If the user runs \Make specifying \cmd{main.exe} as the desired output, \Make
will first build \cmd{util.o} and \cmd{main.o}, in any order since the
corresponding tasks are independent, and will then build \cmd{main.exe}. If the
user modifies the sources of the utility library and runs \Make again, it will
perform a \emph{full rebuild}, because all three tasks transitively depend on
the library, as illustrated in Fig.~\ref{fig-make}(b). On the other hand, if the
user modifies \cmd{main.c} then a \emph{partial rebuild} is sufficient: indeed,
the file \cmd{util.o} does not need to be rebuilt, since its inputs have not
changed, see Fig.~\ref{fig-make}(c). Note that if the dependency graph is
\emph{acyclic} then each task needs to be executed at most once. Cyclic task
dependencies are typically not allowed in build systems although there are rare
exceptions, see~\S\ref{sec-iterative-compute}.

@@

\begin{figure}[h]
\begin{subfigure}[b]{0.90\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/shake-example.pdf}}
\caption{Dependency graph produced after the previous build.}
\end{subfigure}
\begin{subfigure}[b]{0.90\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/shake-example-rebuild.pdf}}
\caption{Since \cmd{docs.txt} has changed, we rebuild \cmd{release.txt} and
\cmd{release.tar}, discovering a new dependency.}
\end{subfigure}
\caption{Dynamic dependencies example: create \cmd{README} and add it to the
list of release documents \cmd{docs.txt}.\label{fig-shake}}
\end{figure}

@@

\vspace{1mm}
\begin{minted}[xleftmargin=10pt]{haskell}
"release.tar" %> \_ -> do
    need ["release.txt"]
    files <- lines <$> readFile "release.txt"
    need files
    system "tar" $ ["-cf", "result.tar"] ++ files
\end{minted}
\vspace{1mm}
